\input{../header}
\input{header-en}
\immediate\write18{pdflatex eng212-22.tex}
\immediate\write18{convert -density 150 -adaptive-resize 480x480 eng212-22.pdf eng212-22.jpg}
%
%
\begin{document}\begin{minipage}[b][14cm][t]{\textwidth}
%%%
\begin{center}\large\BT{高二下学期末英语考试二部分第二节}\end{center}
\begin{center}\Large Being yourself\end{center}
\begin{large}
Do you always \QD{follow} others in what you are wearing,what you do and never \QD{have} your own decisions in your life?\\[3pt]
Almost in every school a 'top' crowd sets the pace\zh{(领先)},while the others follow their lead.Let's say the top crowd \TK{decides} that it is smart to wear bright red sweaters. Pretty soon everybody is wearing \TK{a} bright red sweater.There is nothing wrong with that, except the fact that on some people bright red sweater is \TK{extremely} unbecoming \zh{(不得体的)}. The situation can even become \TK{dangerous}, if the top crowd determines that it is smart to drink or to drive cars at seventy miles an hour. Then the people \TK{who} follow the lead \QD{are risking} their lives. They \QD{are like} the sheep \DY{being led} \TK{to} the butcher\zh{(屠夫)}.\\[3pt]
Now, chances are that you have \QD{come across} situations like these
\QD{more than} once in your life; chances are that one time or \TK{another} you probably did something \DY{you knew to be wrong}. You may have excused \TK{yourself} by saying, "Gee, the crowd does it. " Well, let the crowd do it, but don't do it yourself. Learn to say, " No".\QD{Develop your own standards and your own judgments}. \TK{If} you know the crowd is planning some- thing you \TK{disagreed} to, have the courage to bow \zh{(鞠躬)} out politely. You'll have the satisfaction of \QD{standing} on your own two feet.
\end{large}
%%%
\end{minipage}\end{document}
